---
title: "Iron And Steel"
author: "Yudi Mao"
date: "9/30/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

## Iron&Steel import changes from major countries through 2015-2018

Data used is from data of import of the United States.(https://usatrade.census.gov/data)

```{r}
library(tidyverse)
library(readxl)
library(magrittr)

#Input data
usaimport_ds <- read_xlsx("usaimport.xlsx")
colnames(usaimport_ds) <- c("Commodity","Country","Time","Money")

#Filter the subset
iron_steel <- filter(usaimport_ds, Commodity == "72 Iron And Steel")

#Transfor money to per million
iron_steel$Money <- round(as.numeric(iron_steel$Money) / 1000000, 1)
```

## Pic.1 Import throughout a year

We use average import per month to predict 2018.

```{r}
#Predict 2018
iron_steel$Time[which(iron_steel$Time == "2018 through July")] <- "predicted 2018"
iron_steel$Money[which(iron_steel$Time == "2018")] <- round(iron_steel$Money[which(iron_steel$Time == "predicted 2018")]*12/7, 1)

year_ds <- filter(iron_steel, Time %in% c("2015", "2016", "2017", "predicted 2018"))

#Histogram of different countries and areas
ggplot(data = year_ds) +
  geom_bar(mapping = aes(x = Time, y = Money, fill = Country), stat = "identity") +
  ggtitle("Import of different countries and areas per year, by Yudi Mao")
```

From this histogram, we can roughly conclude that iron&steel import from China decreased these years, especially 2016 compared to 2015. Import from European Union roughly remained the same level, although its predicted amount of 2018 will also decrease, but slightly.

However, we notice that the amount of iron&steel import from European Union is far larger than others, which makes other countries hard to intepret. Meanwhile, we have drawed conclusion between China and EU. Thus:

In next histogram, EU will be removed, and other countries will be showed in their proportion of import of the United States.

## Pic.2 Proportion of each country (European Union excluded)

```{r}
#Exclude EU
year_ds_euex <- filter(year_ds, Country != "European Union")

#Histogram of proportion
ggplot(data = year_ds_euex) +
  geom_bar(mapping = aes(x = Time, y = Money, fill = Country), stat = "identity", position = "fill") +
  ggtitle("Import proportion of different countries per year, by Yudi Mao")
```

In pic.2, we can roughly conclude that inport from China decreased from 2015-2017, while inport from Germany and Italy increased. Other countries roughly remained the same level.

## Pic.3 Line chart of inport per month of China and European Union through 2017-2018

In this picture, we will only use data of China and EU, but more precise from yearly data to monthly data.

```{r}
#data of China and EU per month
month_ds <- filter(iron_steel, !Time %in% c("2015", "2016", "2017", "predicted 2018"))
month_ds <- filter(month_ds, Country %in% c("China", "European Union"))

#Curve the line
ggplot(data = month_ds) +
  geom_bar(mapping = aes(x = Time, y = Money, fill = Country), stat = "identity", position = "dodge") +
  ggtitle("Import of China and EU per month, by Yudi Mao") +
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
```

Roughly, both import from China and EU per month fluctuated among 2017-2018.


