---
title: "Assignment 3"
author: "Tianying Xu"
date: "September 26, 2018"
output: pdf_document
linkcolor: red
urlcolor: blue
citecolor: green
---

```{r setup, include=FALSE}
library(knitr)
library(tidyverse)
opts_chunk$set(echo = TRUE)
```


Data

I am interested in importation of U.S. from other countries in the silk field. Thus, I filter the raw data to importation of silk only, then omit the NAs, finally filter data to only monthly amount. 

```{r}
pacman::p_load(readxl)
library(dplyr)
D=read_xlsx("usaimport.xlsx",skip=3,col_names=c("Commodity","Country","Time","Money"))  %>%
  filter(Commodity=="50 Silk, Including Yarns And Woven Fabric Thereof") %>%
  na.omit() %>%
  filter(Time>"A")
```



Data visulization and analysis

For importation trend in the silk field, I would love to compare the importation amount of several countries to discover the whole trend.

```{r}
t_l=unique(D$Time)
D$Time=factor(D$Time,levels=t_l,ordered = TRUE)

ggplot(D,mapping = aes(x=Time,y=Money))+
  geom_point(aes(colour=factor(Country)))+
  geom_line(aes(group=Country),colour="grey")+
  theme(axis.text.x=element_text(angle=90),plot.title = element_text(hjust = 0.5)) +
  labs(title="Importation of silk --Tianying Xu")
```

This plot indicates importation of silk from several countries from January 2017 to July 2018. From this plot, we could see that there are patterns in importation of China, European Union and Italy, and the amount of these countries are large. Also, Italy has the similar trend with European Union because Italy is a big part of importation from European Union. For France, Germany, Spain and United Kingdom, the amount is relatively small. Thus, I will choose China and European Union to do a deeper analysis.


```{r}
D1=D %>%
  select(Country,Time,Money) %>%
  filter(Country=="China" | Country=="European Union")

ggplot(D1,mapping = aes(x=Time,y=Money,fill=factor(Country)))+
  geom_bar(position="dodge",stat = "identity")+
  theme(axis.text.x=element_text(angle=90),plot.title = element_text(hjust = 0.5)) +
  labs(title="Importation of silk --Tianying Xu")
```

This bar plot describe the importation of Chine and European Union during January 2017 to July 2018. From this plot, we could see that on average, importation from Europre Union is slightly higher than from China. Also, when importation from China decreases, importation from European Union increases, like the cases in Feburary 2017, June 2017, July 2017, October 2017 and March 2018. Although importation from China decreases in March 2018, it increases later, which may not be affected by the tariffs.

Conclusion

China and European union are the main source of silk to U.S. among these selected countries, and they are of similar amount every month. Also, there is not clear evidence in the silk field that tariffs affect the amount of importation.




